---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# baqgarchutil

**!! THIS PACKAGE IS STILL IN EARLY DEVELOPEMENT !!**

The goal of baqgarchutil is to provide utility functions for mGJR class 
objects from the ([mgarchBEKK](https://github.com/vst/mgarchBEKK) package. 
This includes performing a test for detecting conditional heteroscedasticity, 
analysing the residuals of a fitted mGJR model and applying/plotting a 
News Impact Function.

Needs to be addressed before final release:
1.  reformat code for `march_test` and `mch_diag`
2.  update manual for `march_test` and `mch_diag`
3.  vertical plotting in `baq_niplot` needs apropriate parameters (par)
4.  implement a `baq_resplot` or a wrapper function to analyze the
    residuals of a fitted mGJR class object with qqplots and the 
    `mch_diag` function


## Installation

You can install baqgarchutil from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("sebinum/baqgarchutil")
```

## Example

Examples will be included once all planned functions have been implemented.

```{r example}
## basic example code
```
