---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# baqgarchutil

[![Travis Build Status](https://api.travis-ci.org/sebinum/baqgarchutil.svg?branch=master)](https://travis-ci.org/sebinum/baqgarchutil)
[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/baqgarchutil)](https://cran.r-project.org/package=baqgarchutil)

## Overview

The goal of baqgarchutil is to provide utility functions for mGJR class 
objects from the 
[mgarchBEKK](https://cran.r-project.org/web/packages/mgarchBEKK/index.html) 
package and making the process of identifying conditional heteroscedasticity, 
performing residual diagnostics and visualizing the results of a news impact 
on the conditional covariance matrices as convenient as possible.

## Installation

You can install baqgarchutil from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("sebinum/baqgarchutil")
```

## Example / Usage

Each function in this package contains an example on how to use it. The next
release will most likely contain a vignette with more background on the use
and interpretation of a plotted news impact on volatility.
