---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# baqgarchutil

**!! THIS PACKAGE IS STILL IN EARLY DEVELOPEMENT !!**

The goal of baqgarchutil is to provide utility functions for mGJR class 
objects from the mgarchBEKK package. This includes performing a test for 
detecting conditional heteroscedasticity, analysing the residuals of a 
fitted mGJR model and applying/plotting a News Impact Function.

Needs to be addressed before release:
\enumerate{
 \item reformat code for \code{march_test} and \code{mch_diag}
 \item update manual for \code{march_test} and \code{mch_diag}
}

## Installation

You can install baqgarchutil from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("sebinum/baqgarchutil")
```

## Example

Examples will be included once all planned functions have been implemented.

```{r example}
## basic example code
```
